---
title: "MATH 60610"
author: "Jonathan Andrew Guay, Sébastien Caron, William Delisle, Xavier Marcoux"
date: "2023-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Objective

The objective is to improve a naive trading strategy with machine learning.


# Initialization

If required, run use run_install_packages.R to install the packages required for the project.

```{r}
library("here")
# Source the functions and librairies
source(here("Function", "f_source_functions.R"))

f_source_functions()

```
# CLustering

To begin, We use a clustering algorithm on the stocks of the NASDAQ100 in 2007.
For the features, we used various accounting numbers and ratios.
The raw data is from the compustat database.

```{r}
# Retrieve and clean the data used for the clustering algorithm
f_clean_data_clustering()

# Run the clustering algorithm (K-mean, 10)
stocks_symbols <- f_cluster(10)

```
# Collect and clean data

Once the stocks are determined, we will retrieve raw data for the prices and the volatility.
1) The price data is from quantmod (yahoo finance)
2) The volatility data is from otpion metrics database.

(Note: information to retrieve the raw data files from the vendors is under an appropriate README file in the raw data folder.)

```{r}
# Retrieve stock information from quantmod for each ticker.
  priceData <- get_stock_data(stocks_symbols)
  
  summary(priceData)
  
  # Save the 'data' object to an RData file
  save(priceData, file = here("Clean_Data", "stock_data.rda"))
  
  # Store the volatility data
  df_vol <- f_get_vol_data()
  
  # Store price data
  df_price <- f_get_price_data()  
  
```

# Create the pairs

At this step, we create all possible pairs and store their corresponding price and volatility data.
We proceed to create the price ratios and the volatility ratios.  
Furthermore, we compute the technical indicators used for the trading algorithm. 
(100 day moving average and 2 standard deviation rolling window)

Regressions are also estimated.


```{r}
list_ratios_technicals <- f_compute_ratios_technicals(stocks_symbols, 100, 2, df_vol, df_price)

# Example
print(tail(list_ratios_technicals[[1]]))

```
# Run naive strategy (in sample)
Can skip this step if not required, rda file already saved.

```{r}
# Generate the in-sample data to train the classification
f_run_strategy(start_date="2008-01-01", end_date="2017-12-31", list_ratios_technicals, strategy="naive")
# Create classification features for the trades
f_create_training_data_classification(start_date="2008-01-01", end_date="2017-12-31")
```

# Regression

En ce moment cest deja integrer dans la fonction list_ratios_technicals

# Classification
Run the classification algorithm on the trades retrieved from the naive strategy (in-sample).
Integrate the required features to the database of indicators

```{r}
classification_model <- f_train_classification()

```


# Run all strategies (out of sample)

```{r}
# Create the backtest for a strategy
f_run_strategy(start_date="2018-01-01", end_date="2022-12-31", list_ratios_technicals, strategy="naive")
f_run_strategy(start_date="2018-01-01", end_date="2022-12-31", list_ratios_technicals, strategy="regression")
# f_run_strategy(start_date="2018-01-01", end_date="2022-12-31", list_ratios_technicals, strategy="classification")
# f_run_strategy(start_date="2018-01-01", end_date="2022-12-31", list_ratios_technicals, strategy="both")
```

# Load the out-of-sample results
Instead of running all the strategies, simply load the existing RDA files containing the results.

```{r}

equity_curves <- f_load_equity_curves()
all_trades <- f_load_trades()
```


# Results

Show results

```{r}
# Display the results
risk_metrics <- f_risk_metrics(equity_curves, all_trades)
print(risk_metrics["Portfolio_statistics"])
print(risk_metrics["Trades_statistics"])

```






